Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-14 paper/paper.tex
Small fix in Table 9
final final pass

In particular, we were not able to reuse the \smonkey tests on the
\hermes engine. This happened because \smonkey has its own assertion
framework, but \hermes did not interpret these assertions, resulting
in failures in all test executions from this engine. These failures
did not happen when the \smonkey tests were transplanted to the other engines,
though.

@@

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',}, column ``Engine'' shows the
affected engine, column ``Status'' shows the status of the bug report
at the time of the writing. The status string appears in bold face for
status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
Column ``Severity'' shows the severity of confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test. Considering severity levels, we found that
\jsc~\cite{jsc-severity} and \smonkey{}~\cite{mozilla-severity}
developers use five levels, whereas \chakra{}~\cite{chakra-severity}
and \veight{}~\cite{v8-severity} developers use only three. As usual,
the smallest the number the highest the severity of the bug. We use a
dash (``-'') in place of the severity level for the cases where the
bug report is pending confirmation. Of the \noBugsTransplantation{}
bugs we reported in this experiment,
\noBugsTransplantationConfirmed\ were promoted from the status ``New''
to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are
severity-2 bugs.  Although we did not find any critical bugs, most of
the bugs are seemingly important as per the categorization given by
engineers. Analyzing the issue tracker of \chakra, we found that
severity-1 bugs are indeed rare. Considering the number of bug reports
confirmed by developers, \chakra{} was the engine with the highest
number: \bugsChakra{}, with \bugsChakraFixed{} bugs fixed. Considering
the remaining engines, \veight{} developers confirmed the
\noTransVeightBugsReported{} bugs we reported, fixing
\noTransVeightBugsFixed{}. Curiously, Google engineers confirmed the
issued bug reports in a few hours. Likewise, we reported only one bug
on Mozilla's \smonkey, which was quickly fixed.  Overall, we found
that development teams of other engines, specially \jsc, took much
longer to analyze bug reports as can be observed in the \jsc\ stacked
bar from Figure~\ref{fig:stacked-engine}. However, once the team
confirmed those bugs they were then quickly fixed.

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the fuzzing tool used
(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
bug report (``Status'')\Comment{ as of Aug. 24, 2018, the URL of the bug report
(``URL'')}, the severity of the bug report (``Sev.''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. For \veight{},
we reported \noDiffVeight{} bugs,
all of them confirmed, with \noDiffVeightFixed{} fixed.

>>>>

%In particular, we were not able to reuse the \smonkey tests on the
%\hermes engine. This happened because \smonkey has its own assertion
%framework, but \hermes did not interpret these assertions, resulting
%in failures in all test executions from this engine. These failures
%did not happen when the \smonkey tests were transplanted to the other engines,
%though.

@@

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',}, column ``Engine'' shows the
affected engine, column ``Status'' shows the status of the bug report
at the time of the writing. The status string appears in bold face for
status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
Column ``Severity'' shows the severity of confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test. Considering severity levels, we found that
\jsc~\cite{jsc-severity} and \smonkey{}~\cite{mozilla-severity}
developers use five levels, whereas \chakra{}~\cite{chakra-severity}
and \veight{}~\cite{v8-severity} developers use only three. As usual,
the smallest the number the highest the severity of the bug. We use a
dash (``-'') in place of the severity level for the cases where the
bug report is pending confirmation. Of the 32
bugs we reported in this experiment,
\noBugsTransplantationConfirmed\ were promoted from the status ``New''
to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are
severity-2 bugs.  Although we did not find any critical bugs, most of
the bugs are seemingly important as per the categorization given by
engineers. Analyzing the issue tracker of \chakra, we found that
severity-1 bugs are indeed rare. Considering the number of bug reports
confirmed by developers, \chakra{} was the engine with the highest
number: \bugsChakra{}, with \bugsChakraFixed{} bugs fixed. Considering
the remaining engines, \veight{} developers confirmed the
\noTransVeightBugsReported{} bugs we reported, fixing
\noTransVeightBugsFixed{}. Curiously, Google engineers confirmed the
issued bug reports in a few hours. Likewise, we reported only one bug
on Mozilla's \smonkey, which was quickly fixed.  Overall, we found
that development teams of other engines, specially \jsc, took much
longer to analyze bug reports as can be observed in the \jsc\ stacked
bar from Figure~\ref{fig:stacked-engine}. However, once the team
confirmed those bugs they were then quickly fixed.

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the fuzzing tool used
(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
bug report (``Status'')\Comment{ as of Aug. 24, 2018, the URL of the bug report
(``URL'')}, the severity of the bug report (``Sev.''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{} using differential
testing; the bugs we found
were duplicates and were not reported. For \veight{},
we reported \noDiffVeight{} bugs,
all of them confirmed, with \noDiffVeightFixed{} fixed.
